Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-07-11 Submission.Rmd
updating regression tables

cr_burn_m1 <- lm(scale(burnout) ~ scale(overall.challenge_center), modreg)
#summary(cr_burn_m1)

cr_burn_m2 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
#summary(cr_burn_m2)

cr_burn_m3 <- lm(scale(burnout) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_burn_m3)

@@

cr_stress_m1 <- lm(scale(stress) ~ scale(overall.challenge_center), modreg)
#summary(cr_stress_m1)

cr_stress_m2 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_stress_m2)

cr_stress_m3 <- lm(scale(stress) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_stress_m3)

@@

cr_eng_m1 <- lm((engagement) ~ scale(overall.challenge_center), modreg)
#summary(cr_eng_m1)

cr_eng_m2 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_eng_m2)

cr_eng_m3 <- lm((engagement) ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_eng_m3)

@@

hr_burn_m1 <- lm((burnout) ~ scale(overall.hindrance_center), modreg)
#summary(hr_burn_m1)

hr_burn_m2 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_burn_m2)

hr_burn_m3 <- lm((burnout) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_burn_m3)

@@

hr_stress_m1 <- lm((stress) ~ scale(overall.hindrance_center), modreg)
#summary(hr_stress_m1)

hr_stress_m2 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_stress_m2)

hr_stress_m3 <- lm((stress) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_stress_m3)

@@

hr_eng_m1 <- lm((engagement) ~ scale(overall.hindrance_center), modreg)
#summary(hr_eng_m1)

hr_eng_m2 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_eng_m2)

hr_eng_m3 <- lm((engagement) ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_eng_m3)

@@

# b weights
chal.2.burn <- round(summary(cr_burn_m2)$coefficients[2, 1],2)
res.2.burn <- round(summary(cr_burn_m2)$coefficients[3, 1],2)

int.cr.3.burn <- round(summary(cr_burn_m3)$coefficients[4, 1],2)

@@

int.cr.3.stress <- round(summary(cr_stress_m3)$coefficients[4, 1],2)

@@

int.cr.3.eng <- round(summary(cr_eng_m3)$coefficients[4, 1],2)

@@

# b weights
hind.2.burn <- round(summary(hr_burn_m2)$coefficients[2, 1],2)
res.2hr.burn <- round(summary(hr_burn_m2)$coefficients[3, 1],2)

int.hr.3.burn <- round(summary(hr_burn_m3)$coefficients[4, 1],2)

@@

int.hr.3.stress <- round(summary(hr_stress_m3)$coefficients[4, 1],2)

@@

int.hr.3.eng <- round(summary(hr_eng_m3)$coefficients[4, 1],2)

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))

@@

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance X Resource")
Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress,"**"), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(res.2hr.burn,"*"), paste(int.hr.3.burn,"**"))
R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), paste(hr_burn_m3_r,"**"))
#DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
DeltaR <- c("","",hr_eng_r_square_change, "","",paste(hr_stress_r_square_change,"**"), "","",paste(hr_burn_r_square_change, "**"))
regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))

>>>>

cr_burn_m1 <- lm(burnout ~ scale(overall.challenge_center), modreg)
#summary(cr_burn_m1)

cr_burn_m2 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource), modreg)
#summary(cr_burn_m2)

cr_burn_m3 <- lm(burnout ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_burn_m3)

@@

cr_stress_m1 <- lm(stress ~ scale(overall.challenge_center), modreg)
#summary(cr_stress_m1)

cr_stress_m2 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_stress_m2)

cr_stress_m3 <- lm(stress ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_stress_m3)

@@

cr_eng_m1 <- lm(engagement ~ scale(overall.challenge_center), modreg)
#summary(cr_eng_m1)

cr_eng_m2 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center), modreg)
#summary(cr_eng_m2)

cr_eng_m3 <- lm(engagement ~ scale(overall.challenge_center) + scale(overall.resource_center) + scale(overall.challenge_center*overall.resource_center), modreg)
#summary(cr_eng_m3)

@@

hr_burn_m1 <- lm(burnout ~ scale(overall.hindrance_center), modreg)
#summary(hr_burn_m1)

hr_burn_m2 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_burn_m2)

hr_burn_m3 <- lm(burnout ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_burn_m3)

@@

hr_stress_m1 <- lm(stress ~ scale(overall.hindrance_center), modreg)
#summary(hr_stress_m1)

hr_stress_m2 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_stress_m2)

hr_stress_m3 <- lm(stress ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_stress_m3)

@@

hr_eng_m1 <- lm(engagement ~ scale(overall.hindrance_center), modreg)
#summary(hr_eng_m1)

hr_eng_m2 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center), modreg)
#summary(hr_eng_m2)

hr_eng_m3 <- lm(engagement ~ scale(overall.hindrance_center) + scale(overall.resource_center) + scale(overall.hindrance_center*overall.resource_center), modreg)
#summary(hr_eng_m3)

@@

# b weights
chal.2.burn <- round(summary(cr_burn_m2)$coefficients[2, 1],2)
res.2.burn <- round(summary(cr_burn_m2)$coefficients[3, 1],2)
chal.3.burn <- round(summary(cr_burn_m3)$coefficients[2, 1],2)
res.3.burn <- round(summary(cr_burn_m3)$coefficients[3, 1],2)
int.cr.3.burn <- round(summary(cr_burn_m3)$coefficients[4, 1],2)

@@

chal.3.stress <- round(summary(cr_stress_m3)$coefficients[2, 1],2)
res.3.stress <- round(summary(cr_stress_m3)$coefficients[3, 1],2)
int.cr.3.stress <- round(summary(cr_stress_m3)$coefficients[4, 1],2)

@@

chal.3.eng <- round(summary(cr_eng_m3)$coefficients[2, 1],2)
res.3.eng <- round(summary(cr_eng_m3)$coefficients[3, 1],2)
int.cr.3.eng <- round(summary(cr_eng_m3)$coefficients[4, 1],2)

@@

# b weights
hind.2.burn <- round(summary(hr_burn_m2)$coefficients[2, 1],2)
res.2hr.burn <- round(summary(hr_burn_m2)$coefficients[3, 1],2)
hind.3.burn <- round(summary(hr_burn_m3)$coefficients[2, 1],2)
res.3hr.burn <- round(summary(hr_burn_m3)$coefficients[3, 1],2)
int.hr.3.burn <- round(summary(hr_burn_m3)$coefficients[4, 1],2)

@@

hind.3.stress <- round(summary(hr_stress_m3)$coefficients[2, 1],2)
res.3hr.stress <- round(summary(hr_stress_m3)$coefficients[3, 1],2)
int.hr.3.stress <- round(summary(hr_stress_m3)$coefficients[4, 1],2)

@@

hind.3.eng <- round(summary(hr_eng_m3)$coefficients[2, 1],2)
res.3hr.eng <- round(summary(hr_eng_m3)$coefficients[3, 1],2)
int.hr.3.eng <- round(summary(hr_eng_m3)$coefficients[4, 1],2)

@@

DV <- c("Engagement","","","","","Stress","","","","", "Burnout","","","","")
Step <- c("1", "","2", "", "", "1", "","2", "","", "1", "","2", "","")
Model <- c("Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), chal.3.eng, paste(res.3.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, chal.3.stress, res.3.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, paste(chal.3.burn,"**"), res.3.burn, int.cr.3.burn)
R2 <- c("", paste(cr_eng_m2_r,"**"), "", "", paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), "", "", round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), "", "",paste(round(cr_burn_m3_r,2),"**"))
DeltaR <- c("","","","", paste(cr_eng_r_square_change,"*"), "","","","",cr_stress_r_square_change, "","","","",cr_burn_r_square_change)
regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))

@@

DV <- c("Engagement","","","","","Stress","","","","", "Burnout","","","","")
Step <- c("1", "","2", "", "", "1", "","2", "","", "1", "","2", "","")
Model <- c("Hindrance", "Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance", "Resource", "Hindrance X Resource", "Hindrance", "Resource", "Hindrance", "Resource", "Hindrance X Resource")
Beta <- c(paste(hind.2.eng,"**"), paste(res.2hr.eng,"**"), paste(sigfill(hind.3.eng),"**"), paste(res.3hr.eng,"**"), int.hr.3.eng, paste(sigfill(hind.2.stress),"*"), paste(res.2hr.stress), paste(hind.3.stress, "**"), paste(sigfill(res.3hr.stress)), paste(int.hr.3.stress,"**"), paste(sigfill(hind.2.burn),"*"), paste(sigfill(res.2hr.burn),"*"), paste(sigfill(hind.3.burn),"*"), paste(res.3hr.burn), paste(int.hr.3.burn,"**"))
R2 <- c("", paste(round(hr_eng_m2_r,2),"**"), "", "", paste(round(hr_eng_m3_r,2),"**"), "", paste(hr_stress_m2_r,"*"), "", "", paste(hr_stress_m3_r, "**"), "", paste(hr_burn_m2_r,"**"), "", "", paste(hr_burn_m3_r,"**"))
#DeltaR <- c("",paste(hr_eng_m2_r,"**"),hr_eng_r_square_change, "",paste(hr_stress_m2_r,"**"),hr_stress_r_square_change, "",paste(hr_burn_m2_r,"**"),hr_burn_r_square_change)
DeltaR <- c("","","","",hr_eng_r_square_change, "","","","",paste(hr_stress_r_square_change,"**"), "","","","",paste(hr_burn_r_square_change, "**"))
regtable <- as.data.frame(cbind(DV, Step, Model, Beta, R2, DeltaR))

### 2024-07-11 Submission.tex
updating regression tables

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Challenge & -0.08 &  & \\
 &  & Resource & 0.37 ** & 0.15 ** & \\
 & 2 & Challenge & -0.07 * & 0.16 ** & 0.01 *\\
Stress & 1 & Resource & 0.14 &  & \\
 &  & Challenge X Resource & -0.07 & 0.01 & \\
 & 2 & Challenge & 0.02 & 0.01 & 0.00\\
Burnout & 1 & Resource & 0.33 ** &  & \\
 &  & Challenge & -0.14 & 0.04 ** & \\
 & 2 & Resource & 0.06 & 0.04 ** & 0.00\\
Engagement & 1 & Challenge X Resource & -0.08 &  & \\
 &  & Challenge & 0.37 ** & 0.15 ** & \\
 & 2 & Resource & -0.07 * & 0.16 ** & 0.01 *\\
Stress & 1 & Challenge & 0.14 &  & \\
 &  & Resource & -0.07 & 0.01 & \\
 & 2 & Challenge X Resource & 0.02 & 0.01 & 0.00\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Hindrance & -0.11 ** &  & \\
 &  & Resource & 0.35 ** & 0.17 ** & \\
 & 2 & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
Stress & 1 & Hindrance & 0.08 * &  & \\
 &  & Resource & 0.01 ** & 0.01 * & \\
 & 2 & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
Burnout & 1 & Hindrance & 0.09 * &  & \\
 &  & Resource & 0.1 * & 0.04 ** & \\
 & 2 & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
\bottomrule
\addlinespace
\end{tabular}

>>>>

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Challenge & -0.08 &  & \\
 &  & Resource & 0.37 ** & 0.15 ** & \\
 & 2 & Challenge & -0.08 &  & \\
 &  & Resource & 0.37 ** &  & \\
 &  & Challenge X Resource & -0.07 * & 0.16 ** & 0.01 *\\
Stress & 1 & Challenge & 0.12 &  & \\
 &  & Resource & -0.06 & 0.01 & \\
 & 2 & Challenge & 0.12 &  & \\
 &  & Resource & -0.06 &  & \\
 &  & Challenge X Resource & 0.02 & 0.01 & 0.00\\
Burnout & 1 & Challenge & 0.28 ** &  & \\
 &  & Resource & -0.12 & 0.04 ** & \\
 & 2 & Challenge & 0.28 ** &  & \\
 &  & Resource & -0.12 &  & \\
 &  & Challenge X Resource & 0.05 & 0.04 ** & 0.00\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{tabular}{llllll}
\toprule
DV & \multicolumn{1}{c}{Step} & \multicolumn{1}{c}{Model} & \multicolumn{1}{c}{$\beta$} & \multicolumn{1}{c}{$R^2$} & \multicolumn{1}{c}{$\Delta R^2$}\\
\midrule
Engagement & 1 & Hindrance & -0.11 ** &  & \\
 &  & Resource & 0.35 ** & 0.17 ** & \\
 & 2 & Hindrance & -0.10 ** &  & \\
 &  & Resource & 0.34 ** &  & \\
 &  & Hindrance X Resource & -0.01 & 0.17 ** & 0.00\\
Stress & 1 & Hindrance & 0.08 * &  & \\
 &  & Resource & 0.01 & 0.01 * & \\
 & 2 & Hindrance & 0.16 ** &  & \\
 &  & Resource & -0.10 &  & \\
 &  & Hindrance X Resource & -0.17 ** & 0.04 ** & 0.03 **\\
Burnout & 1 & Hindrance & 0.09 * &  & \\
 &  & Resource & 0.10 * & 0.04 ** & \\
 & 2 & Hindrance & 0.13 * &  & \\
 &  & Resource & 0.03 &  & \\
 &  & Hindrance X Resource & -0.11 ** & 0.05 ** & 0.01 **\\
\bottomrule
\addlinespace
\end{tabular}
